---
title: "Coke Zero vs Pepsi Zero/Max — Reddit Difference-in-Differences"
format: pdf
execute:
  echo: true
  warning: false
  message: false
---

```{r setup}
if (!requireNamespace("here", quietly = TRUE))
  install.packages("here", repos = "https://cloud.r-project.org")

library(here)
library(readr)
library(dplyr)
library(stringr)
library(tidyverse)

reddit <- read_csv("/Users/codyzheng_1/Desktop/my-r-project/data/coke_pepsi_reddit_all.csv")
glimpse(reddit)
```

## Exercise 2(c)

```{r}
#| label: ex-2c-filter
reddit |>
  filter(subreddit == "cocacola") |>
  glimpse()
```

## Exercise 2(d)

```{r}
#| label: ex-2d-summary
# (1) Total row count
nrow(reddit)

# (2) Share of posts vs. comments
reddit |>
  count(type) |>
  mutate(share = n / sum(n))

# (3) Date range of created_utc
range(as.POSIXct(reddit$created_utc, origin = "1970-01-01", tz = "UTC"))
```

## Exercise 2(e)

```{r}
#| label: ex-2e-slice
cocacola <- reddit |>
  filter(subreddit == "cocacola") |>
  mutate(date = format(as.POSIXct(created_utc, origin = "1970-01-01", tz = "UTC"), "%Y-%m-%d"))

top3_comments <- cocacola |> filter(type == "comment") |> arrange(created_utc) |> slice(1:3)
top3_posts    <- cocacola |> filter(type == "post")    |> arrange(created_utc) |> slice(1:3)

bind_rows(top3_comments, top3_posts) |>
  select(type, subreddit, author, title, text, score, date)
```

```{r}
#| label: ex-2e-typeset
#| results: asis
print_rows <- function(df, section_title) {
  cat(sprintf("### %s\n\n", section_title))
  for (i in seq_len(nrow(df))) {
    r        <- df[i, ]
    raw_text <- if (is.na(r$text)) "" else r$text
    body     <- if (nchar(trimws(raw_text)) == 0) "*[no text]*" else raw_text
    score    <- if (is.na(r$score)) "NA" else as.character(r$score)
    title    <- if (is.na(r$title)) "" else r$title
    if (r$type == "post" && nchar(trimws(title)) > 0) {
      cat(sprintf("**%s | u/%s | r/%s | score: %s | %s**\n\n",
                  title, r$author, r$subreddit, score, r$date))
    } else {
      cat(sprintf("**[comment] u/%s | r/%s | score: %s | %s**\n\n",
                  r$author, r$subreddit, score, r$date))
    }
    cat(body, "\n\n---\n\n")
  }
}

print_rows(top3_comments, "Earliest 3 Comments — r/cocacola")
print_rows(top3_posts,    "Earliest 3 Posts — r/cocacola")
```

## Exercise 3(a)

```{r}
#| label: ex-3a-strip
text_orig <- reddit$text

clean_text <- function(x) {
  x |>
    str_remove_all("\\[([^\\]]+)\\]\\([^)]+\\)") |>
    str_replace_all("\\[([^\\]]+)\\]\\([^)]+\\)", "\\1") |>
    str_remove_all("https?://\\S+") |>
    str_remove_all("(?i)\\bu/\\S+") |>
    str_remove_all("(?i)\\br/\\S+") |>
    str_remove_all("[*_`]+") |>
    str_remove_all("(?m)^#+\\s*") |>
    str_replace_all("&amp;",  "&") |>
    str_replace_all("&lt;",   "<") |>
    str_replace_all("&gt;",   ">") |>
    str_replace_all("&quot;", "\"") |>
    str_replace_all("&nbsp;", " ") |>
    str_replace_all("[ \t]+", " ") |>
    str_trim()
}

chars_before <- sum(nchar(reddit$text), na.rm = TRUE) +
                sum(nchar(reddit$title), na.rm = TRUE)

reddit <- reddit |>
  mutate(
    text  = clean_text(text),
    title = clean_text(title)
  )

chars_after <- sum(nchar(reddit$text), na.rm = TRUE) +
               sum(nchar(reddit$title), na.rm = TRUE)

cat(sprintf(
  "Characters before cleaning: %s\nCharacters after cleaning:  %s\nCharacters removed:         %s\n",
  format(chars_before, big.mark = ","),
  format(chars_after,  big.mark = ","),
  format(chars_before - chars_after, big.mark = ",")
))
```

## Exercise 3(b)

```{r}
#| label: ex-3b-pass1
n_before <- nrow(reddit)
reddit   <- distinct(reddit, text, author, .keep_all = TRUE)
n_after  <- nrow(reddit)
cat(sprintf("Pass 1 (cross-posting: same text + author)\n  Before:  %d\n  After:   %d\n  Dropped: %d\n",
            n_before, n_after, n_before - n_after))
```

```{r}
#| label: ex-3b-pass2
n_before <- nrow(reddit)
reddit   <- distinct(reddit, text, subreddit, .keep_all = TRUE)
n_after  <- nrow(reddit)
cat(sprintf("Pass 2 (coordinated: same text + subreddit)\n  Before:  %d\n  After:   %d\n  Dropped: %d\n",
            n_before, n_after, n_before - n_after))
```

```{r}
#| label: ex-3b-write
write_csv(reddit, "/Users/codyzheng_1/Desktop/my-r-project/data/coke_pepsi_reddit_cleaned.csv")
cat(sprintf("Wrote %d rows to data/coke_pepsi_reddit_cleaned.csv\n", nrow(reddit)))
```

## Exercise 4

We set up an OpenAI API key at platform.openai.com, loaded \$19 of credit, and saved the key as `OPENAI_API_KEY` in `~/.Renviron`. The key was verified with `Sys.getenv("OPENAI_API_KEY")` in the R console. We use the OpenAI API rather than Anthropic's because at the time of writing, `gpt-5-mini` is roughly one-quarter the price of Claude Haiku, and the GABRIEL methodology we follow uses OpenAI throughout.

## Exercise 5

```{r}
#| label: ex-5-trim
reddit <- read_csv("/Users/codyzheng_1/Desktop/my-r-project/data/coke_pepsi_reddit_cleaned.csv",
                   show_col_types = FALSE)

threshold <- quantile(nchar(reddit$text), 0.99, na.rm = TRUE)

n_before <- nrow(reddit)
reddit   <- reddit |> filter(is.na(text) | nchar(text) <= threshold)
n_after  <- nrow(reddit)

cat(sprintf("Cleaned CSV rows : %d\nTrimmed CSV rows : %d\nDropped          : %d\n",
            n_before, n_after, n_before - n_after))

write_csv(reddit, "/Users/codyzheng_1/Desktop/my-r-project/data/coke_pepsi_reddit_trimmed.csv")
```

The top 1% of posts by character length were removed, dropping 539 rows from 54,445 to 53,906. Posts in the top 1% contain at least \~1,500 words, versus a median of \~34 words — roughly 45x longer than typical posts.

## Exercise 6

```{r}
#| label: ex-6-cost
# (a) AI cost estimate
n               <- nrow(reddit)
avg_tok         <- mean(nchar(reddit$text), na.rm = TRUE) / 4
fixed_prompt_in <- 800
T_in            <- n * (avg_tok + fixed_prompt_in)
tokens_out      <- 30
T_out           <- n * tokens_out
p_in            <- 0.25
p_out           <- 2.00
floor_h         <- T_in / 200000 / 60
cost            <- T_in / 1e6 * p_in + T_out / 1e6 * p_out

# (b) Human cost estimate
total_words  <- sum(str_count(reddit$text, "[^[:space:]]+"), na.rm = TRUE)
wpm          <- 238
min_per_item <- 2
wage         <- 15
platform_fee <- 0.20
n_trim       <- n
human_hours  <- (total_words / wpm + n_trim * min_per_item) / 60
human_cost   <- human_hours * wage * (1 + platform_fee)

cat(sprintf(
"=== AI vs Human Comparison ===
AI hours   : %.1f h       Human hours : %.0f h     Time reduction  : %.1f%%
AI cost    : $%.2f       Human cost  : $%.0f    Cost reduction  : %.1f%%\n",
  floor_h, human_hours, (human_hours - floor_h) / human_hours * 100,
  cost,    human_cost,  (human_cost  - cost)    / human_cost  * 100
))
```

The AI approach costs \$15.59 and takes 4.1 hours at the rate-limit floor, compared to \$38,118 and 2,118 person-hours for a human annotator — a 99.8% reduction in time and near-total cost elimination. At this scale, manual labeling is economically infeasible; LLMs make the analysis tractable.

## Exercise 7

Each row in the trimmed corpus was classified using a single API call to `gpt-5-mini`. The prompt instructed the model to determine whether the text contained a complaint specifically about the row's focal beverage (Coke Zero for treatment rows, Pepsi Zero/Max for control rows), and if so, to extract a verbatim 3–8 word phrase naming the complaint subject. Neutral mentions, recipes, questions, and praise of other brands were explicitly excluded. The production script (`code/reddit_classification.R`) used parallel processing with 10 workers via the `furrr` package and a checkpoint system to allow resumption after interruption.

```{r}
#| label: ex-7-summary
extracted <- read_csv("/Users/codyzheng_1/Desktop/my-r-project/data/coke_pepsi_reddit_extracted_42000.csv",
                      show_col_types = FALSE)

cat(sprintf(
"=== Classification Summary ===
Total rows        : %d
Complaints        : %d (%.1f%%)
Non-empty subject : %d\n",
  nrow(extracted),
  sum(extracted$is_complaint == TRUE, na.rm = TRUE),
  mean(extracted$is_complaint == TRUE, na.rm = TRUE) * 100,
  sum(nchar(extracted$complaint_subject) > 0, na.rm = TRUE)
))
```

## Exercise 8

```{r}
#| label: ex-8-load
reddit <- read_csv("/Users/codyzheng_1/Desktop/my-r-project/data/coke_pepsi_reddit_bucketed.csv",
                   show_col_types = FALSE)

cat(sprintf("Total rows: %d\n", nrow(reddit)))
cat(sprintf("Coke Zero complaints: %d\n",
            sum(reddit$group == "treatment" & reddit$is_complaint == TRUE, na.rm = TRUE)))

cat("\nBucket counts (Coke Zero complaints):\n")
reddit |>
  filter(group == "treatment", is_complaint == TRUE) |>
  count(complaint_bucket, sort = TRUE) |>
  print(n = 20)
```

The bucketing procedure followed a two-stage pipeline. In Stage 1, all unique `complaint_subject` phrases from Coke Zero complaints were sent in a single API call to `gpt-5.5` with high reasoning effort, which proposed 16 mutually exclusive bucket categories following GABRIEL guidelines (specific, directional, non-overlapping). In Stage 2, `gpt-5.4-mini` classified each phrase into one of the 16 buckets using batch API calls of 100 phrases each. The bucket schema was saved to `data/coke_pepsi_reddit_buckets_meta.json`.

## Exercise 4

We set up an OpenAI API key at platform.openai.com, loaded \$19 of credit, and saved the key as `OPENAI_API_KEY` in `~/.Renviron`. The key was verified with `Sys.getenv("OPENAI_API_KEY")` in the R console. We use the OpenAI API rather than Anthropic's because at the time of writing, `gpt-5-mini` is roughly one-quarter the price of Claude Haiku, and the GABRIEL methodology we follow uses OpenAI throughout.

## Exercise 5

```{r}
#| label: ex-5-trim
reddit <- read_csv("/Users/codyzheng_1/Desktop/my-r-project/data/coke_pepsi_reddit_cleaned.csv",
                   show_col_types = FALSE)

threshold <- quantile(nchar(reddit$text), 0.99, na.rm = TRUE)

n_before <- nrow(reddit)
reddit   <- reddit |> filter(is.na(text) | nchar(text) <= threshold)
n_after  <- nrow(reddit)

cat(sprintf("Cleaned CSV rows : %d\nTrimmed CSV rows : %d\nDropped          : %d\n",
            n_before, n_after, n_before - n_after))

write_csv(reddit, "/Users/codyzheng_1/Desktop/my-r-project/data/coke_pepsi_reddit_trimmed.csv")
```

The top 1% of posts by character length were removed, dropping 539 rows from 54,445 to 53,906. Posts in the top 1% contain at least \~1,500 words versus a median of \~34 words — roughly 45x longer than a typical post.

## Exercise 6

```{r}
#| label: ex-6-cost
# (a) AI cost estimate
n               <- nrow(reddit)
avg_tok         <- mean(nchar(reddit$text), na.rm = TRUE) / 4
fixed_prompt_in <- 800
T_in            <- n * (avg_tok + fixed_prompt_in)
tokens_out      <- 30
T_out           <- n * tokens_out
p_in            <- 0.25
p_out           <- 2.00
floor_h         <- T_in / 200000 / 60
cost            <- T_in / 1e6 * p_in + T_out / 1e6 * p_out

# (b) Human cost estimate
total_words  <- sum(str_count(reddit$text, "[^[:space:]]+"), na.rm = TRUE)
wpm          <- 238
min_per_item <- 2
wage         <- 15
platform_fee <- 0.20
n_trim       <- n
human_hours  <- (total_words / wpm + n_trim * min_per_item) / 60
human_cost   <- human_hours * wage * (1 + platform_fee)

cat(sprintf(
"=== AI vs Human Comparison ===
AI hours   : %.1f h       Human hours : %.0f h     Time reduction  : %.1f%%
AI cost    : $%.2f       Human cost  : $%.0f    Cost reduction  : %.1f%%\n",
  floor_h, human_hours, (human_hours - floor_h) / human_hours * 100,
  cost,    human_cost,  (human_cost  - cost)    / human_cost  * 100
))
```

The AI approach costs \$15.59 and takes 4.1 hours at the rate-limit floor, compared to \$38,118 and 2,118 person-hours for a human annotator — a 99.8% reduction in time and near-total cost elimination. At this scale, manual labeling is economically infeasible; LLMs make the analysis tractable.

## Exercise 7

Each row in the trimmed corpus was classified using a single API call to `gpt-5-mini`. The prompt instructed the model to determine whether the text contained a complaint specifically about the row's focal beverage (Coke Zero for treatment rows, Pepsi Zero/Max for control rows), and if so, to extract a verbatim 3–8 word phrase naming the complaint subject. Neutral mentions, recipes, questions, and praise of other brands were explicitly excluded. The production script (`code/reddit_classification.R`) used parallel processing with 10 workers via the `furrr` package and a checkpoint system to allow resumption after interruption.

```{r}
#| label: ex-7-summary
extracted <- read_csv("/Users/codyzheng_1/Desktop/my-r-project/data/coke_pepsi_reddit_extracted_42000.csv",
                      show_col_types = FALSE)

cat(sprintf(
"=== Classification Summary ===
Total rows        : %d
Complaints        : %d (%.1f%%)
Non-empty subject : %d\n",
  nrow(extracted),
  sum(extracted$is_complaint == TRUE, na.rm = TRUE),
  mean(extracted$is_complaint == TRUE, na.rm = TRUE) * 100,
  sum(nchar(extracted$complaint_subject) > 0, na.rm = TRUE)
))
```

## Exercise 8

The bucketing procedure followed a two-stage pipeline described in the GABRIEL framework. In Stage 1, all unique `complaint_subject` phrases from Coke Zero complaints were sent in a single API call to `gpt-5.5` with high reasoning effort, which proposed 16 mutually exclusive bucket categories (specific, directional, non-overlapping). In Stage 2, `gpt-5.4-mini` classified each phrase into one of the 16 buckets using batch calls of 100 phrases each. The bucket schema was saved to `data/coke_pepsi_reddit_buckets_meta.json`.

```{r}
#| label: ex-8-load
reddit <- read_csv("/Users/codyzheng_1/Desktop/my-r-project/data/coke_pepsi_reddit_bucketed.csv",
                   show_col_types = FALSE)

cat(sprintf("Total rows: %d\n", nrow(reddit)))
cat(sprintf("Coke Zero complaints: %d\n",
            sum(reddit$group == "treatment" & reddit$is_complaint == TRUE, na.rm = TRUE)))

cat("\nBucket counts (Coke Zero complaints):\n")
reddit |>
  filter(group == "treatment", is_complaint == TRUE) |>
  count(complaint_bucket, sort = TRUE) |>
  print(n = 20)
```

